signalHsmm - a novel semi-Markov model of eukaryotic signal peptides

### 2015-06-17 paper.tex
improved cv section

We selected 13 properties from AAIndex database~\citep{2008kawashimaaaindex} (see Table~\ref{tab:aaprop}), each attributed to a single criterion. We created 96 permutations of the properties, where each permutation contains only one property associated with a given criterion. Considering all permutations of properties, we created 96 possible clusterings of amino acids using Euclidean distance and Ward's method. Further, we cut the clusterings to create four-group encodings.

@@

To compare encodings we performed a 5-fold cross-validation training a new instance of signalHsmm on every encoding. We created balanced data sets by subsampling a number of proteins without a signal peptide equal to the number of proteins with signal peptide. The cross-validation was repeated XXX times, to ensure that every negative protein was tested at least once with XXX probability.

>>>>

We selected 13 properties from AAIndex database~\citep{2008kawashimaaaindex} (see Table~\ref{tab:aaprop}), each attributed to a single criterion. We established 96 permutations of the properties, where each permutation contains only one property associated with a given criterion. Considering all permutations of properties, we created 96 possible clusterings of amino acids using Euclidean distance and Ward's method. Further, we cut the clusterings to create four-group encodings. As expected, some encodings (31\%) were identical.

@@

To compare encodings we performed a 5-fold cross-validation training a new instance of signalHsmm on every encoding. We created balanced data sets by subsampling a number of proteins without a signal peptide equal to the number of proteins with signal peptide.
The analysis was carried using also redundant encodings, but results are not shown (HSMM is a deterministic algorithm and predictions for identical groupings of amino acids were the same). The cross-validation was repeated XXX times, to ensure that every negative protein was tested at least once with XXX probability.

As the performance measure interest we choose
